Supplementary Information: Improving Monocular Depth Estimation with Global Depth Histogram Matching

### 2019-10-18 paper/cvpr2020/supplement.tex
Video folder, ablation study, supplement editing.

\maketitle
\section{Ablation study on number of SID bins}
\begin{itemize}
  \item Simulation: 70, 140, 210, 280 bins
  \item Captured: 70, 140, 210, 280 bins
\end{itemize}
Compare RMSE and runtime.
\section{Ablation study on effect of reflectance estimation}
\begin{itemize}
  \item Intensity used to initialize histogram, not used to move pixels
  \item Intensity used to initialize histogram and move pixels
  \item Intensity not used to initialize histogram, used to move pixels
  \item Intensity not used to initialize histogram, not used to move pixels
\end{itemize}
Compare RMSE and runtime.

>>>>

\maketitle
\section{Ablation study on number of SID bins}
\begin{itemize}
  \item Simulation: 70, 140, 210, 280 bins
  \item Captured: 70, 140, 210, 280 bins
\end{itemize}
Compare RMSE and runtime.
Simulated on NYU Depth v2. DenseDepth, SBR of 100. Only histogram matching
was timed, not the running of the MDE or the denoising pipeline.
\begin{figure}[H]
  \centering
  \begin{tabular}{c|cc}
    \toprule
    \# of sid bins & RMSE & Approx. Time/image (sec) \\
    \midrule
    70  & $0.351$ & $0.24$ \\
    140 & $0.346$ & $0.63$ \\
    210 & $0.345$ & $1.12$ \\
    280 & $0.345$ & $1.84$ \\
    \bottomrule
  \end{tabular}
\end{figure}

\section{Ablation study on effect of reflectance estimation}
Simulated on NYU v2. DenseDepth, 140 bins. SPAD simulation uses intensity, SBR
of 100.
\begin{itemize}
  \item Intensity used to initialize histogram, not used to move pixels
  \item Intensity used to initialize histogram and move pixels
  \item Intensity not used to initialize histogram, used to move pixels
  \item Intensity not used to initialize histogram, not used to move pixels
\end{itemize}
Compare RMSE and runtime.
\begin{figure}[H]
  \centering
  \begin{tabular}{c|c|cc}
    \toprule
    Intensity-weighted histogram & Intensity-aware pixel movement & Avg. RMSE & Approx. Time/image (sec) \\
    \midrule
    \multirow{2}{*}{Yes} & Yes & $0.346$ & $4.6$ \\
                         & No & $0.346$ & $0.6$ \\
    \midrule
    \multirow{2}{*}{No} & Yes & $0.444$ & $4.7$ \\
                        & No & $0.444$ & $0.6$ \\
    \bottomrule
  \end{tabular}
  \caption{Ablation study on simulated data for NYU Depth v2. When the SPAD
    is simulated with the reflectance info but no reflectance estimate is used
    to generate a weighted histogram from the CNN depth map, the results are
    significantly worse. Furthermore, the pixel movement procedure need not take
  into account the weights of the pixels being moved, since doing so provides no
improvement and can take appreciably longer than a vectorized implementation
that does not take pixel weights into account.}
\end{figure}
